### 2016-05-12 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor edits to hose stream and gas burner reports

Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}. The meter consists of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0--4.1 MPa (0--600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate. The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\% for the pressure sensor~\cite{Akron:2009}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate. The total expanded uncertainty was estimated at $\pm10$\%. 
% FIND FLOW METER REFERENCE
\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Pictures/flow_meter}
	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
	\label{fig:flow_meter}
\end{figure}
\FloatBarrier

@@

\subsection{Monitor Experiments}
\label{sec:monitor_procedure}
Three experiments, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream. Test 1 occurred in the Single Story Structure, and Tests 2 and 3 occurred in the Two Story Structure. A fourth experiment, Test 4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively. The monitor was always set to flow water from a fixed position. Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure and provided a baseline to compare the impact of the motion of the nozzle on the air movement through the structure.

Test 1 utilized a monitor equipped with a combination nozzle to flow water from Room C of the Single Story Structure to the area above the doorway on the south wall of Room B (Fig.~\ref{fig:test_1_pic}). A plan view of the structure's layout annotated with the approximate location of the bi-directional probe array used to measure gas velocity through an interior doorway and the general direction of the fully established flow path for Test 1 can be found in Fig.~\ref{fig:east_setup}. The procedure for Test 1 was the simplest of all the test procedures. First, water was flowed in a straight stream pattern for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally the stream was changed to a wide fog stream for 30 seconds. The procedure was repeated an additional time.

@@

% Add flow chart? %
Tests 2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure. The nozzle was aimed at two targets during the series: a ``near'' target located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target located approximately 3.7~m (12~ft) from the interior side of the north wall. The procedure for each test began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. This entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_2_3_pic} contains images of each type of hose stream aimed at the near and far targets.

@@

% Where was the handline aimed? Add flow chart? %
Tests 6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. Test 6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each experiment began by using a straight stream to flow water in a fixed, horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth left-to-right), clockwise, and counterclockwise application patterns. This entire process was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test 6 with the flow path fully established.

@@

% ===========
% = RESULTS =
% ===========

@@

\section{Monitor Experiments}
\label{sec:monitor_results}

Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns during Test 2. Similar plots of the average measured velocity through the interior doorway for Tests 1, 3, and 4 are presented in Appendix~\ref{chap:monitor_plots}. Additionally, Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 1--4.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity through the interior stairwell door (A10) during Test 2 for the three hose stream patterns.}
	\label{fig:Test_2_BDP_A10_Avg_All}
\end{figure}

\begin{table}[!ht]
\caption{Average air velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{5}{c}{\large ------------------------ 120 gpm ------------------------} 
\\
 & \underline{Test 1} & \multicolumn{2}{c}{\underline{Test 2}} & \multicolumn{2}{c}{\underline{Test 3}}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & -0.3 $\pm0.1$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 1.0 $\pm0.2$ & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 2.4 $\pm0.4$ & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
\\ \midrule
 & \multicolumn{2}{c}{\large --- 180 gpm ---} & \multicolumn{3}{c}{} 
\\
 & \multicolumn{2}{c}{\underline{Test 4}} & \multicolumn{3}{c}{} 
\\
\textbf{Stream} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\multicolumn{3}{c}{} 
\\
\midrule
\textit{Straight} & 1.7 $\pm0.3$ & 1.9 $\pm0.3$ & \multicolumn{3}{c}{} 
\\ \multicolumn{6}{c}{} \\
\textit{Smooth Bore} & 1.7 $\pm0.3$ & 2.0 $\pm0.4$ & \multicolumn{3}{c}{}
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

% StdDev Values
% \midrule
% \textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
% \\ \multicolumn{6}{c}{} \\
% \textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
% \\ \multicolumn{6}{c}{} \\
% \textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
% \\ \midrule
%  & \multicolumn{2}{c}{\large --- 180 gpm ---} & \multicolumn{3}{c}{} 
% \\
%  & \multicolumn{2}{c}{\underline{Test 4}} & \multicolumn{3}{c}{} 
% \\
% \textbf{Stream} &
% \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
% \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
% \multicolumn{3}{c}{} 
% \\
% \midrule
% \textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
% \\ \multicolumn{6}{c}{} \\
% \textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
% \\
% \bottomrule

Looking at the table and figures, a number of trends can be observed. For example, there was significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test 1. Also, looking at Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities through the interior doorway when the flow path was fully established compared to the straight stream. This trend is also observed above in Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} and in Figs.~\ref{fig:Test_1_BDP_A6_Avg_All}~and~\ref{fig:Test_3_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}. Furthermore, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream. Finally, the Test 4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle equipped with a 1 in tip produce approximately the same amount of air movement through the interior doorway.
\FloatBarrier

\section{Handline Experiments}
\label{sec:handline_results}

Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern (back and forth left-to-right), a clockwise rotation, and counterclockwise rotation during Test 6. Similar plots of the average measured velocity through the interior doorway for Tests 5 and 7 are presented in Appendix~\ref{chap:handline_plots}. Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 5 and Tests 6-7, respectively.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
	\caption{Average velocity through stairwell door during Test 6 for the three hose stream patterns.}
	\label{fig:Test_6_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

% #######################
% # East Handline Table #
% #######################

\begin{table}[!ht]
\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Test 5}
\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{3}{c}{\underline{Room A}} & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & 0.2 $\pm0.04$ & 0.6 $\pm0.1$ & 0.8 $\pm0.1$ & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.5 $\pm0.1$
\\ \multicolumn{7}{c}{} \\
\textit{Narrow Fog} & 1.7 $\pm0.3$ & 1.8 $\pm0.3$ & 1.6 $\pm0.3$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.3$
\\ \multicolumn{7}{c}{} \\
\textit{Wide Fog} & 1.9 $\pm0.3$ & 2.1 $\pm0.4$ & 2.2 $\pm0.4$ & 2.1 $\pm0.4$ & 2.3 $\pm0.4$ & 2.6 $\pm0.5$
\\ \bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

% StdDev values
% \\ \midrule
% \textit{Straight} & 0.2 $\pm0.3$ & 0.6 $\pm0.2$ & 0.8 $\pm0.3$ & -0.1 $\pm0.1$ & 0.5 $\pm0.3$ & 0.5 $\pm0.2$
% \\ \multicolumn{7}{c}{} \\
% \textit{Narrow Fog} & 1.7 $\pm0.4$ & 1.8 $\pm0.2$ & 1.6 $\pm0.1$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.2$
% \\ \multicolumn{7}{c}{} \\
% \textit{Wide Fog} & 1.9 $\pm0.2$ & 2.1 $\pm0.1$ & 2.2 $\pm0.1$ & 2.1 $\pm0.3$ & 2.3 $\pm0.1$ & 2.6 $\pm0.1$
% \\ \bottomrule

% #######################
% # West Handline Table #
% #######################

\begin{table}[!ht]
\caption{Average air velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{\underline{Test 6}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.2 $\pm0.04$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 0.4 $\pm0.1$ & 1.0 $\pm0.2$ & 0.8 $\pm0.1$ & 1.0 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
\\ \midrule
 & \multicolumn{4}{c}{\underline{Test 7}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.6 $\pm0.1$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.1$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
\\ \bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}

>>>>

Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}. The meter consists of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0--4.1 MPa (0--600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate. The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\% for the pressure sensor~\cite{Akron:2009}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate. The total expanded uncertainty was estimated at $\pm10$\%.

\begin{figure}[!ht]
	\includegraphics[width=4in]{../Figures/Pictures/flow_meter}
	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
	\label{fig:flow_meter}
\end{figure}
\FloatBarrier

@@

\subsection{Monitor Experiments}
\label{sec:monitor_procedure}
Three experiments, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream. Test~1 occurred in the Single Story Structure, and Tests~2 and 3 occurred in the Two Story Structure. A fourth experiment, Test~4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively. The monitor was always set to flow water from a fixed position. Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure and provided a baseline to compare the impact of the motion of the nozzle on the air movement through the structure.

Test~1 utilized a monitor equipped with a combination nozzle to flow water from Room~C of the Single Story Structure to the area above the doorway on the south wall of Room~B (Fig.~\ref{fig:test_1_pic}). A plan view of the structure's layout during Test~1 can be found in Fig.~\ref{fig:east_setup}. The figure highlights the general direction of the established flow path along with the approximate location of A6, the bi-directional probe array used to measure gas velocity through the northeast interior doorway. The procedure for Test~1 was the simplest of all the test procedures. First, water was flowed in a straight stream for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally the stream was changed to a wide fog for 30 seconds. The procedure was repeated an additional time.

@@

Tests 2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure. The nozzle was aimed at two targets during the series: a ``near'' target located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target located approximately 3.7~m (12~ft) from the interior side of the north wall. The procedure for each test began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. This entire process was repeated using the narrow fog and wide fog streams. Fig.~\ref{fig:test_2_3_pic} contains images of each type of hose stream aimed at the near and far targets.

@@

Tests 6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. Test 6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each experiment began by using a straight stream to flow water in a fixed, horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth left-to-right), clockwise, and counterclockwise application patterns. This entire process was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test 6 with the flow path fully established.

@@

% ==========================
% = RESULTS AND DISCUSSION =
% ==========================

@@

\section{Monitor Experiments}
\label{sec:monitor_results}
Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} contains a plot of the average gas velocity measured by the bi-directional probes in the array at the interior stairwell door (A10) for the straight stream, narrow fog stream, and wide fog stream during Test~2. Similar plots of the average measured velocity through the interior doorway for Tests~1, 3, and 4 are presented in Appendix~\ref{chap:monitor_plots}. Additionally, Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and target location combination studied during Tests~1--4.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
	\caption[Average gas velocity through the interior stairwell door during Test 2 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 2 for the three hose stream patterns.}
	\label{fig:Test_2_BDP_A10_Avg_All}
\end{figure}

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lcccccccc}
\toprule
 &  & \multicolumn{7}{c}{\large ----------------------------- 120 gpm -----------------------------} 
\\
 &  & \underline{Test 1} &  & \multicolumn{2}{c}{\underline{Test 2}} &  & \multicolumn{2}{c}{\underline{Test 3}}
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
\\ 
\midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   & -0.3 $\pm0.1$   & & 0.9 $\pm0.2$    & 0.9 $\pm0.2$    & & 0.7 $\pm0.1$    & 0.7 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.1 $\pm0.2$  & &   0.9 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.7 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   2.4 $\pm0.4$  & &   1.2 $\pm0.2$  & 1.3 $\pm0.2$    & &   0.9 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
\\ \midrule
 &  & \multicolumn{3}{c}{\large ------ 180 gpm ------} & \multicolumn{4}{c}{} 
\\
 &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &
 \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}} &
\multicolumn{4}{c}{} 
\\
\midrule
\multirow{2}{*}{\textit{Straight}} &
\small{m/s}   &   1.7 $\pm0.3$   & \multicolumn{2}{c}{1.9 $\pm0.3$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (-0.7 $\pm0.1$) & \multicolumn{2}{c}{(-0.7 $\pm0.1$)} & \multicolumn{4}{c}{} 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Smooth Bore}} &
\small{m/s}   &   1.7 $\pm0.3$  &  \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (-0.7 $\pm0.1$) & \multicolumn{2}{c}{(-0.7 $\pm0.1$)} & \multicolumn{4}{c}{} 
\\
% \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
% \begin{tabular}{@{}c@{}} -0.3 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} & & 
% \begin{tabular}{@{}c@{}} 0.9 $\pm0.2$ \\ (-0.7 $\pm0.1$) \end{tabular} & 
% \begin{tabular}{@{}c@{}} 0.9 $\pm0.2$ \\ (-0.7 $\pm0.1$) \end{tabular} & & 
% \begin{tabular}{@{}c@{}} 0.7 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} & 
% \begin{tabular}{@{}c@{}} 0.7 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} 
% \\ \multicolumn{9}{c}{} \\
% \textit{Narrow Fog} & \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
% 1.1 $\pm0.2$ & & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & & 0.8 $\pm0.1$ & 0.7 $\pm0.1$
% \\ \multicolumn{9}{c}{} \\
% \textit{Wide Fog} & \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
% 2.4 $\pm0.4$ & & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
% \\ \midrule
%  &  & \multicolumn{3}{c}{\large --- 180 gpm ---} & \multicolumn{4}{c}{} 
% \\
%  &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
% \\
% \textbf{Stream} & \textbf{Units} &
% \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &  &
% \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
% \multicolumn{4}{c}{} 
% \\
% \midrule
% \textit{Straight} &  \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
% 1.7 $\pm0.3$ &  & 1.9 $\pm0.3$ & \multicolumn{4}{c}{} 
% \\ \multicolumn{9}{c}{} \\
% \textit{Smooth Bore} & 
% 1.7 $\pm0.3$ &  & 2.0 $\pm0.4$ & \multicolumn{4}{c}{}
% \\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

Looking at the table and figures, a number of trends can be observed. For example, there was significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test~1. Looking at Table~\ref{table:all_mon_vel_avgs}, the narrow fog and wide fog streams caused higher velocities through the interior doorway when the flow path was fully established compared to the straight stream. This trend can also be seen graphically in Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} and Figs.~\ref{fig:Test_1_BDP_A6_Avg_All}~and~\ref{fig:Test_3_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}. Furthermore, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream. Finally, the Test 4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that the straight stream from a combination nozzle and the solid stream from a smooth bore nozzle equipped with a 1~in tip produced approximately the same amount of air movement through the interior doorway.
\FloatBarrier

\section{Handline Experiments}
\label{sec:handline_results}
Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} contains a plot of the average gas velocity measured by the bi-directional probes in the array at the interior stairwell door (A10) for the straight stream, narrow fog stream, and wide fog stream being applied in a fixed position, a sweeping pattern (back and forth, left-to-right), a clockwise rotation, and a counterclockwise rotation during Test 6. Similar plots of the average measured velocity through the interior doorway for Tests 5 and 7 are presented in Appendix~\ref{chap:handline_plots}. Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and application pattern combination studied during Test 5 and Tests 6 and 7, respectively.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
	\caption[Average gas velocity through the interior stairwell door during Test 6 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 6 for the three hose stream patterns.}
	\label{fig:Test_6_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

\begin{table}[!ht]
\caption{Average gas velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for Test 5}
\begin{tabular}{lccccccc}
\toprule
 & \multicolumn{3}{c}{\underline{Room A}} &  & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} &  & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & 0.2 $\pm0.04$ & 0.6 $\pm0.1$ & 0.8 $\pm0.1$ &  &
-0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.5 $\pm0.1$
\\ \multicolumn{8}{c}{} \\
\textit{Narrow Fog} & 1.7 $\pm0.3$ & 1.8 $\pm0.3$ & 1.6 $\pm0.3$ &  & 
0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.3$
\\ \multicolumn{8}{c}{} \\
\textit{Wide Fog} & 1.9 $\pm0.3$ & 2.1 $\pm0.4$ & 2.2 $\pm0.4$ &  & 
2.1 $\pm0.4$ & 2.3 $\pm0.4$ & 2.6 $\pm0.5$
\\ \bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

\begin{table}[!ht]
\caption{Average gas velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{\underline{Test 6}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.2 $\pm0.04$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 0.4 $\pm0.1$ & 1.0 $\pm0.2$ & 0.8 $\pm0.1$ & 1.0 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
\\ \midrule
 & \multicolumn{4}{c}{\underline{Test 7}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.6 $\pm0.1$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.1$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
\\ \bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}
\FloatBarrier
